---
title: "ForageFish EDI submission"
author: "S. G. Glancy"
date: "12/9/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



```{r}


require(utils)
require(tibble)
require(dplyr)
require(ggplot2)
require(lubridate)
require(janitor)
require(tidyverse)

require(readr)

Concat_Count <- read_csv("C:/Users/Sarah/Desktop/Glancy/LTER/2021_EDIprep/Concat_Count.csv")


Concat_Meas <- read_csv("C:/Users/Sarah/Desktop/Glancy/LTER/2021_EDIprep/Concat_Meas.csv")


Station_lookup_truncate2 <- read_csv("C:/Users/Sarah/Desktop/Glancy/LTER/2021_EDIprep/Station_lookup_truncate2.csv")
```
need to change BEGIN_GMT_TOWDATE in ISO 8601 format, YYYY-MM-DD HH:MM:SS

```{r}

Station_lookup_truncate2$BEGIN_GMT_TOWDATE <- parse_date_time(Station_lookup_truncate2$BEGIN_GMT_TOWDATE, "mdyHM")

```

read in CSVs for data (measurements and counts) and for station (data from NOAA
) using readr

Join based on cruise number and station number. 

for join() in R need same column headers. 

change column headers in station table from CRUISE6 to "Cruise" and STATION to "Station



###

now I want all of my x values (meas or count) to be returned, but only the y (station values) that match to the meas/count. 

will try a left join first. 



```{r}

Concat_Count$station = as.numeric(as.character(Concat_Count$station))


## got a warning baout NAs by coercion

Concat_Count_Stationjoin <- Concat_Count %>%
  left_join(Station_lookup_truncate2,by= c("cruise", "station")
  )

```

worked, do the other one then figure out how to export as CSV. Print.to()?

```{r}


# indicated cruise and station are both numeric, should be okay

Concat_Meas_Stationjoin <- Concat_Meas %>%
  left_join(Station_lookup_truncate2,by= c("cruise", "station")
  )


```

GREAT. that worked too. now need to export as CSVs. 


```{r}
ITIS_lookup <- read_csv("C:/Users/Sarah/Desktop/Glancy/LTER/2021_EDIprep/ITIS_lookup.csv")


ITIS_lookup <- remove_empty(ITIS_lookup, which  = c("cols"))



```

great that works.

```{r}

Concat_Count_Stationjoin <- Concat_Count_Stationjoin %>%
mutate(Llopiz_taxa = (if_else(is.na(preySpp), if_else(is.na(preyTaxa), preyTaxon, preyTaxa), preySpp) ))



```

needed to add the assignment (<-) to make it work, but the joining column is created.  do the same for the _Meas table

```{r}

Concat_Meas_Stationjoin <- Concat_Meas_Stationjoin %>%
mutate(Llopiz_taxa = (if_else(is.na(preySpp), if_else(is.na(preyTaxa), preyTaxon, preyTaxa), preySpp) ))




```

Now do the L join based on the column Llopiz taxa

```{r}
Concat_Count_EDI <- Concat_Count_Stationjoin %>%
  left_join(ITIS_lookup,by= "Llopiz_taxa"
  )
view(Concat_Count_EDI)

Concat_Meas_EDI <- Concat_Meas_Stationjoin %>%
  left_join(ITIS_lookup,by= "Llopiz_taxa"
  )
view(Concat_Meas_EDI)

```

Everything is there. would be good to remove columns (year, author, name credibility and usage)

```{r}
Concat_Count_EDI <- select(Concat_Count_EDI,  - NameUsage, -Credibility)

view(Concat_Count_EDI)

Concat_Meas_EDI <- select(Concat_Meas_EDI, - NameUsage, -Credibility)

view(Concat_Meas_EDI)
```


FIN

write files

```{r}
write.csv(Concat_Count_EDI, "C:/Users/Sarah/Desktop/Glancy/LTER/2021_EDIprep/ForageFish_EDI/Concat_Count_EDI.csv")

write.csv(Concat_Meas_EDI, "C:/Users/Sarah/Desktop/Glancy/LTER/2021_EDIprep/ForageFish_EDI/Concat_Meas_EDI.csv")


```








